\documentclass[a4paper,9.5 pt]{extarticle}


%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  STARTING HERE, DO NOT TOUCH ANYTHING 
%%%%%%% --------------------------------------------------------------------------------------

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\usepackage{anyfontsize}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

%%%% Set Margins
\usepackage[margin=1cm, top=1cm, bottom= 1cm]{geometry}

%%%% Set Fonts
\setmainfont{Times New Roman}

%%%% Set Page
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color
\definecolor{UI_blue}{RGB}{32, 64, 151}

%%%% Define New Commands
\usepackage[style=nature, maxbibnames=3]{biblatex}
\addbibresource{Publications.bib}

%%%% Bold Name in Publications
\renewcommand*{\mkbibnamegiven}[1]{%
\ifitemannotation{highlight}
{\textbf{#1}}
{#1}}

\renewcommand*{\mkbibnamefamily}[1]{%
\ifitemannotation{highlight}
{\textbf{#1}}
{#1}}

%%%% Set Sections formatting
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-10pt} \hrulefill \vspace{-6pt}]

%%%% Set Subtext Formatting
\newcommand{\subtext}[1]{
#1\par\vspace{-0.2cm}}

%%%% Set Item Spacing
\setlist[itemize]{align=parleft,left=0pt..1em}

%%%% New Itemize "Zitemize" Formatting - tighter spacing than itemize
\newenvironment{zitemize}{
\begin{itemize}\itemsep0pt \parskip0pt \parsep1pt}
{\end{itemize}\vspace{-0.5cm}}

%%%% Define Skills Bold Formatting
\newcommand{\hskills}[1]{
\textbf{\bfseries #1} }

\newcommand{\sectioncentered}[1]{%
  \section*{\centering #1} % Centered section title without numbering
  \addcontentsline{toc}{section}{#1} % Ensures it appears in TOC
  \vspace{0.2cm} % Adjust spacing if needed
}


%%%% Set Subsection formatting
\titleformat{\subsection}{\vspace{-0.1cm} 
\bfseries \fontsize{11pt}{2cm}}{}{0em}{}[\vspace{-0.2cm}]

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  END OF "DO NOT TOUCH" REGION
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------

\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{{\LARGE Pranavi Kuntrapakam}} \\
  {\itshape \large Aspiring Fullstack \& ML Engineer} \\
  \rule{\textwidth}{0.5pt} % Horizontal line
  \vspace{1pt} % Adjusted spacing below the line
  \href{mailto:pkuntrapakam@connect.ust.hk}{Email: pkuntrapakam@connect.ust.hk} ~|~
  \href{https://www.linkedin.com/in/pranavi-kuntrapakam/}{LinkedIn: pranavi-kuntrapakam} ~|~
  \href{https://github.com/pranavi-apk}{Github: pranavi-apk}
\end{center}
\vspace{-0.75cm} % Reduced space between header and Education section

%-----------EDUCATION-----------------
\section{EDUCATION}
\textbf{The Hong Kong University of Science and Technology} \hfill Hong Kong \\
Bachelor of Engineering - Computer Engineering with an Extended Major in Artificial Intelligence \hfill 2023 - 2027
\vspace{-0.25cm}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  SKills
%%%%%%% --------------------------------------------------------------------------------------
\section{SKILLS SUMMARY}
\noindent
\textbf{Languages:} Python, TypeScript, JavaScript, C++, HTML, CSS \\
\textbf{Libraries/Frameworks:} React Native, ReactJS, FastAPI, Node.js, Qdrant, Ollama, Streamlit, TensorFlow, PyTorch, Scikit-Learn, Numpy, Pandas, OpenCV, Matplotlib, Tailwind CSS \\
\textbf{Dev Tools:} Postman API, Git, GitHub, Chrome Extension APIs, REST API integration, WebRTC
\vspace{-2mm}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  WORK EXPERIENCE
%%%%%%% --------------------------------------------------------------------------------------
\section{EXPERIENCE}
%%%%%%% ----------------------------------- Role 1 ----------------------------------- %%%%%%%
\subsection*{AI/LLM Developer Intern {\normalsize\normalfont } \hfill Oct 2025 --- Ongoing} 
\subtext{Innocorn AI \hfill HKSTP, Hong Kong SAR} 
    \begin{zitemize}
        \item Developing and enhancing AI-powered chatbot solutions using LLM to improve Kimiyi AI (product of Innocorn)
        \item Implementing workflow automation with n8n to streamline business processes and integrate AI services with existing systems
    \end{zitemize}
    
%%%%%%% ----------------------------------- Role 1 ----------------------------------- %%%%%%%
\subsection*{Talent Foundry Starter {\normalsize\normalfont } \hfill Oct 2025 --- Ongoing} 
\subtext{HKSTP \hfill Hong Kong SAR} 
    \begin{zitemize}
        \item Undergoing advanced training and industry mentorship to develop practical skills in AI, machine learning, and innovation technology for career readiness in Hong Kong’s tech ecosystem.
    \end{zitemize}

%%%%%%% ----------------------------------- Role 1 ----------------------------------- %%%%%%%
\subsection*{Lead Engineer (Founding Team) - Funded 100K HKD by HKSTP {\normalsize\normalfont } \hfill Sep 2025 --- Ongoing} 
\subtext{Stealth Startup (AI Fashion Tech) \hfill Hong Kong SAR} 
    \begin{zitemize}
        \item Architected full-stack AI-powered platform using React Native and Python, integrating machine learning APIs for personalized recommendations.
    \end{zitemize}

%%%%%%% ----------------------------------- Role 1 ----------------------------------- %%%%%%%
\subsection*{AI \& UI/UX Development Intern {\normalsize\normalfont } \hfill Mar 2025 --- Jun 2025} 
\subtext{Voyager Education Ltd \hfill Hong Kong SAR} 
    \begin{zitemize}
        \item Developing \textbf{AI-based projects and educational materials} to integrate AI into STEAM learning.
        \item Enhancing the \textbf{UI/UX design} of Voyager Education’s landing page for a better user experience.
        \item Assisting with consulting projects and proposal development for EdTech initiatives.
    \end{zitemize}


%%%%%%% ----------------------------------- Role 2 ----------------------------------- %%%%%%%
\subsection*{Research and Data Analyst Intern  {\normalsize\normalfont } \hfill Dec 2024 --- Jan 2025} 
\subtext{SoleFit Care Ltd \hfill Remote, HKG} 
    \begin{zitemize}
        \item Collected and processed \textbf{300+ 3D foot sole  datasets} to enhance AI-driven predictive models for manufacturing optimization.
    \item Developed preprocessing scripts in Python to clean and structure raw 3D foot sole data for training CNN models.
    \item Assisted in refining AI algorithms by improving dataset accuracy and feature extraction for model training.
    \end{zitemize}
    
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  ACADEMIC PROJECTS
%%%%%%% --------------------------------------------------------------------------------------

\section{PROJECTS}
\subsection*{Hong Kong Employment \& Financial Legal RAG System \hfill Sep 2025}
    \begin{zitemize}
        \item Built end-to-end RAG pipeline (Python, Qdrant, Ollama) for querying HK case law, with evidence-cited answers via Streamlit UI.
        \item Processed/embedded documents; added semantic search for natural language queries and legal analytics.
    \end{zitemize}
\subsection*{PS: Wish You Were Here --- Virtual Long-Distance Photobooth \hfill Mar 2025}
    \begin{zitemize}
        \item Developed full-stack app (Node.js, WebRTC) for real-time collaborative photo strips, with live mirroring and remote capture.
        \item Created responsive JS/CSS frontend for editing/export; optimized for cross-device performance and privacy.
    \end{zitemize}
\subsection*{Procrasti-NOT Chrome Productivity Extension \hfill Jan 2025}
    \begin{zitemize}
        \item Built/published Chrome extension (JavaScript, Manifest V3) with Pomodoro timer, task manager, and site blocker.
        \item Added persistent storage, badge updates, and motivational overlays for focus enforcement.
    \end{zitemize}

\section{COMPETITIONS} %% (Or "Research", select as appropriate)
%%%%%%% ----------------------------------- Role 1 ----------------------------------- %%%%%%%
\subsection*{\href{https://www.hkstp.org/en/park-life/news-and-events/events/iads-developer-hackathon}{Semi-finalist, IADS Developer Hackathon --- Team Nexus, Hong Kong} \hfill Nov 2025 - Ongoing}
\begin{zitemize}
    \item Led ML engineering for Nexus: AI merchant unification resolving 165K+ fragmented MIDs via NLP \& knowledge graphs on IADS datasets. Built 3-layer architecture enabling fraud detection \& compliance for 15 HK banks
\end{zitemize}

%%%%%%% ----------------------------------- Role 1 ----------------------------------- %%%%%%%
\subsection*{\href{https://www.globalsustainabilitychallenge.org/}{First Prize, Regional Round, Global Sustainability Challenge --- Team Tycoon, Hong Kong} \hfill Nov 2025 - Ongoing}
    \begin{zitemize}
        \item Full Stack Developer working on Resilient360, an integrated disaster management solution that simplifies coordination and accelerates response through a connected and data-driven approach, enabling stakeholders to anticipate risks and strengthen community resilience in times of crisis
    \end{zitemize}
    
\subsection*{\href{https://perma.cc/SEN8-4WUL}{Finalist, Inter-University GenAI Hackathon for SDG --- Team 1101 Mingle, Hong Kong} \hfill Oct 2025}
    \begin{zitemize}
        \item All-in-one app targeted towards the elderly, addressing the problem of elderly isolation and late-life depression in Hong Kong.
        \item Ranked in the \textbf{Top 40 among 200+ teams and Top 10} in our track.
    \end{zitemize}
\subsection*{\href{https://perma.cc/PC7R-5QAS}{Finalist, IET Young Professionals Exhibition \& Competition --- Team UG02, Hong Kong} \hfill Oct 2025}
    \begin{zitemize}
        \item Engineered an \textbf{AI-powered wristband} designed to detect and respond to falls among older adults, promoting safer independent living.
    \end{zitemize}
\subsection*{\href{https://www.linkedin.com/posts/pranavi-kuntrapakam_morganstanley-codetogive-activity-7367492218019831808-IXXx?utm_source=social_share_send&utm_medium=member_desktop_web&rcm=ACoAAER4NqYBt2bGhJj3BPdFNKv2NMuYZSvnmzM}{Finalist, Morgan Stanley Code to Give Hackathon --- Team 8, Hong Kong} \hfill Aug 2025}
    \begin{zitemize}
        \item Highest code contributor, led React Native/TypeScript frontend for \textbf{top-10} team, building workflows and integrating Python/FastAPI backend via REST. Contributed across stack in cross-functional team, emphasizing audio processing, testing, and rapid UI delivery.
    \end{zitemize}
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  VOLUNTEER EXPERIENCE
%%%%%%% --------------------------------------------------------------------------------------
\section{EXTRACURRICULAR ACTIVITIES}  
\textbf{Delegate \& Volunteer} | ReThink HK Sustainability Conference 2025, Hong Kong\\ 
\textbf{Wu Zhi Qiao Team Member} | Bridge to China, HKUST\\ 
\textbf{SENtastic Ambassador} | HKUST\\ 
\textbf{Computer Engineering Peer Mentor} | CPEG, HKUST\\
\textbf{Technical Core Team Member} | Google Developers Group, HKUST \\ 
\textbf{English Language Buddy and Ambassador, Exchange Buddy} | HKUST \\
\vspace{-0.25cm}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  Research
%%%%%%% --------------------------------------------------------------------------------------

\section{RESEARCH} 

\textbf{2026 Happy City Index Researcher for Hong Kong | Happy City Hub | 2025–2026}  \\
Selected as the primary researcher for Hong Kong in a global initiative evaluating urban happiness and well-being. Responsible for data collection, analysis, and assessment of 82+ city indicators across six key dimensions (Citizens, Governance, Environment, Economy, Health, Mobility). Contributing qualitative and quantitative insights for the international Happy City Index report.\\ 
\vspace{+0.25cm}

\textbf{Research Scholar | IRI-NC | 2023}  \\ 
\textit{Role of AI in Finding Habitable Planets}  \\
Conducted a literature review under the guidance of  \textbf{Dr. Robert Malkin (Duke University)} on AI applications in planetary habitability detection.
\vspace{-0.25cm}


\section{CERTIFICATIONS}
Oracle Cloud Infrastructure 2025 Certified AI Foundations Associate\\
Postman API Fundamentals Student Expert\\
Meta Introduction to Front-End Development 

\end{document}

